%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection[page1sidebar]{Recent Work Experience}

\cvexperience{AI Platform Architect / Lead ML Systems Engineer}{Infosis}{Full-time}{Aug 2025 -- Present}{Argentina}

\begin{itemize}
  \item \emphasis{Led the design and implementation of an MCP Server (Model Context Protocol)}, enabling orchestration of LLM-based services with contextual awareness, scalability, and high availability.
  \item \emphasis{Designed AI service platforms integrating LLMs, RAG pipelines, and vector search} using Qdrant as the core retrieval layer.
  \item \emphasis{Built production-grade REST and GraphQL APIs} (Go, Python) to expose AI capabilities to internal systems and mobile clients.
  \item \emphasis{Defined AI platform architecture on Kubernetes}, ensuring observability, reliability, and cost control using Prometheus and Grafana.
  \item \emphasis{Applied Infrastructure as Code (Terraform, Terragrunt)} to provision and operate AI workloads across AWS.
\end{itemize}

\divider

\cvexperience{Lead Software Architect}{Infosis}{Full-time}{Nov 2022 -- Aug 2025}{Argentina}
\begin{itemize}
  \item \emphasis{Designed and led end-to-end ML systems} including computer vision, NLP, and LLM-based solutions deployed in production.
  \item \emphasis{Architected scalable full-stack platforms} combining GraphQL APIs, mobile clients, and cloud-native backends.
  \item \emphasis{Delivered AI-driven systems with measurable business impact}, improving accuracy, performance, and operational efficiency.
  \item \emphasis{Provided technical leadership and architectural guidance} to cross-functional teams, directly contributing to revenue growth.
\end{itemize}

\divider

\cvexperience{Machine Learning Engineer}{Maker Development}{Part-time}{Nov 2023 -- May 2024}{Peru}
\begin{itemize}
  \item \emphasis{Implemented production ML models} for object recognition, facial recognition, NLP, and generative media use cases.
  \item \emphasis{Collaborated on applied AI solutions} focused on real-world deployment, performance, and user experience.
\end{itemize}

\divider

\cvexperience{Senior SRE / DevOps Engineer}{Multiple Companies}{Full-time / Consulting}{2017 -- 2022}{LATAM}
\begin{itemize}
  \item \emphasis{Designed and operated cloud-native platforms} using Kubernetes, Terraform, and AWS at scale.
  \item \emphasis{Built observability, CI/CD, and automation foundations} enabling reliable production systems.
  \item \emphasis{Optimized infrastructure cost and performance} across multiple high-traffic environments.
\end{itemize}